Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-08-07 talk/vmil2012/paper.tex
add description of benchmarks

\usepackage{ifthen}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{relsize}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[colorinlistoftodos]{todonotes}

@@

\todo{a description about what each selected benchmark does}

>>>>

\usepackage{ifthen}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{ulem}
\usepackage{xspace}
\usepackage{relsize}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[pdfpagelabels=true]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}

@@

We used the following benchmarks:

\begin{description}
    \item[chaos:] A Chaosgame implementation creating a fractal.
    \item[crypto\_pyaes:] An AES implementation.
    \item[django:] The templating engine of the Django Web
        framework\footnote{\url{http://www.djangoproject.com/}}.

    \item[go:] A Monte-Carlo Go
        AI\footnote{\url{http://shed-skin.blogspot.com/2009/07/ disco-elegant-python-go-player.html}}.
    \item[pyflate\_fast:] A BZ2 decoder.
    \item[raytrace\_simple:] A ray tracer.
    \item[richards:] The Richards benchmark.
    \item[spambayes:] A Bayesian spam filter\footnote{\url{http://spambayes.sourceforge.net/}}.
    \item[simpy\_expand:] A computer algebra system.
    \item[telco:] A Python version of the Telco decimal
        benchmark\footnote{\url{http://speleotrove.com/decimal/telco.html}},
        using a pure Python decimal floating point implementation.
    \item[twisted\_names:] A DNS server benchmark using the Twisted networking
        framework\footnote{\url{http://twistedmatrix.com/}}.
\end{description}
